Self Regulation Ontology Retest Data: Initial Exploration

### 2017-03-15 SRO_Retest_Analyses.Rmd
minor typo

- Ignore Pearson for now and just focus on Spearman
- Eventually want to get to interclass correlations (between versus within group variability - using anova)
- Clean everything on the whole sample and extract from that. Keep a record of everything that was transformed and whether it was normal at the end

>>>>

- Ignore Pearson for now and just focus on Spearman
- Eventually want to get to intraclass correlations (between versus within group variability - using anova)
- Clean everything on the whole sample and extract from that. Keep a record of everything that was transformed and whether it was normal at the end
